The Exoplanet Orbit Database \textsc{II}: 2014 updates

### 2014-03-19 draft/ms.tex
Minor notes and change fig:koi.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The Exoplanet Orbit Database (EOD) is

@@

We have added an entirely new set of fields for the secondary
eclipse. Previously, due to the limits of instrumentation and limited
sample of exoplanets, there were not much secondary eclipse depth data
available. Since \cite{Wright2011}, as many different surveys have
been launched, more and more secondary eclipse depths at multiple
bands become available for more and more planets. Therefore, we added
this entire new set of fields.

@@

%------------------------------------------------------------------------------
% Figure: single planet page
\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../fig/mass-per-color.eps}
\caption{An example plot produced by the interactive plotting tools of
  EDE on exoplanets.org. The $x$-axis is planet orbital period in days
  and $y$-axis is planet mass in Earth's mass. The exoplanet samples
  being plotted are the ones in the EOD, including transit planets
  (blue large dots), RV planets (red triangles), and timing planets
  (magenta squares). The KOIs are plotted as black small dots, and
  their masses are calculated using their radii based on mass-radius
  relations from the literature (see Section~\ref{sec:orbit}).}
\label{fig:koi}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

The Exoplanet Orbit Database (EOD) is

@@

We have added an entirely new set of fields for the secondary
eclipse. Previously, due to the limits of instrumentation and limited
sample of exoplanets, there were not much secondary eclipse depth data
available. Since \cite{Wright2011}, as many different surveys have
been launched, more and more secondary eclipse depths at multiple
bands become available for more and more planets. Therefore, we added
this entire new set of fields. ZZZ Refer to Ming's SE plot.

@@

%------------------------------------------------------------------------------
% Figure: single planet page
\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../fig/mass-per-interactive.eps}
\caption{ZZZ will change to mass-SEP plot once KOIs have SEP ZZZ
  An example plot produced by the interactive plotting tools of
  EDE on exoplanets.org. The interactive plotting interface is shown
  on the left, with the mass-period plot shown on the right. The
  $x$-axis is planet orbital period in days and $y$-axis is planet
  mass in Earth's mass. The exoplanet samples being plotted are the
  ones in the EOD, including transit planets (blue large dots), RV
  planets (red triangles), and timing planets (magenta squares). The
  KOIs are plotted as black small dots, and their masses are
  calculated using their radii based on mass-radius relations from the
  literature (see Section~\ref{sec:orbit}).}
\label{fig:koi}
\end{figure}

ZZZ add SE plots from Ming
